\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-11-22 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

As noted above, the suggested method implies that the estimation is run at the sector-country level (on top of being mode-year specific), exploiting the variability within each origin country-3d sector pair across 10-d sub-sectors and ports of entry. Yet, it appears that for many couples (country, 3-digit sector), there is too few variability across sub-sectors or ports en entry given the number of fixed effects included in the regression, such that estimation can not be run. This can be seen comparing the number of observations by year/ transport mode with our method / with the referee's method reported in Table \ref{tab_comp_referee1_baseline} (also reported in the online appendix, Section D.3. \textbf{XXX Check XXX}. Put it differently, this methodology discards country-sector pairs that export a limited range of goods to the US and/or which arrive in the USA through the same ports of entry. This may induce a selection bias in the sample covered for estimation. As reported in Table  \ref{tab_comp_referee1_baseline}, the number of pairs covered is much lower (especially in the list of countries covered). This concern is mitigated by noticing that the covered value of trade flows is only slightly lower. If it reduces the sample of sectors and origin countries covered, this method preserves the majority of trade flows in value.

The most important limitation rather comes from the coverage period. Information about the port of entry are only available since 1989, which is already smaller than our full sample starting in 1974. On top of that, because of the Covid situation, the US Bureau of Census was only able to send us the data relative to the years 1997-1999 and 2001-2019. Implementing the referee's method would hence necessarily reduce the time coverage of our analysis by more than 20 years (skipping the 1974-1996 years in particular). In our view, the historical coverage is interesting per se, as it provides useful insights about how transport costs have evolved over time. Eliminating this dimension of the paper would be detrimental to its contribution.

@@

\item[Concern 2] The suggested method features less accuracy in the estimation of the $\beta$.

If we take the value of the $\beta$ by itself, there is no clear criteria to discriminate between the value estimated with our method and the one obtained with the suggested method (when, of course, run on the same sample). Further, as shown in Table \ref{tab_comp_referee1_baseline}, no clear conclusion on a potential upwards or downwards bias that would be attached to our method. Things are more clear-cut in terms of accuracy of the estimation. Specifically, our method yields a more precise estimation of the $\beta$ than the referee's method. To develop on this, for each year and transport mode:
    \begin{itemize}
    \item With the referee's method, we estimate one value for the share of additive component $\beta$ at the $i,s$ level denoted $\hat{\beta}^{ref}_{is(k)}$ associated with a standard deviation $SD_{is}$, by year and transport mode. From this, we can compute the size of the 5-95\% confidence interval $CI^{ref}_{is} = \hat{\beta}_{is}^{max,ref} - \hat{\beta}_{is}^{min,ref}$ where:
        $$\hat{\beta}_{is}^{min,ref} = \hat{\beta}^{ref}_{is(k)} - 1.96 SD_{is},\quad \hat{\beta}_{is}^{max,ref} = \hat{\beta}^{ref}_{is(k)} + 1.96 SD_{is}$$

        \item  Our method provides estimates of the underlying trade costs components ($\widehat{\tau}_i$, $\widehat{\tau}_s$, $\widehat{t}_i$, $\widehat{t}_s$) with an associated matrix of variance-covariance, from which we can rebuild $\beta_{is}$ (on a year-transport mode basis). As such, it does not yield an estimate of $\beta_{is}$ and an associated standard deviation, so that we cannot directly compare the precision of the estimation. We compute the accuracy of the $\beta$ estimate by relying on bootstrap method. Specifically, on a yearly/mode basis we draw a distribution of trade costs components and associated $\beta_{is}$ (10,000 random draws) from which we can compute the mean, the median and the 5-95 confidence interval for each couple $i,s$. Noticing $\beta_{is}^{95}$ and $\beta_{is}^{05}$ the associated thresholds, we then obtain the size of the confidence interval $CI_{is}= \beta_{is}^{95}- \beta_{is}^{05}$.\footnote{Notice that this should be made on the same sample as the one obtained with the referee's method, since the goal is to compare the accuracy of the $\beta_{is}$ estimate - implying to have the same sample of countries / sectors at first. }

@@

    \item We can then evaluate the accuracy of each estimation method by comparing the size of the confidence intervals of the $\beta$, for each couple $i,s$ (by year and transport mode). We summarize this comparison in Figure \ref{fig:accuracy_beta}, which reports the distribution of the ratio of confidence intervals, taken in log.

    \begin{figure}[htbp]
    \caption{Accuracy of the estimation of the $\beta$: Comparison}
    \label{fig:accuracy_beta}
    \begin{center}
    \includegraphics[height=3in]{../../revised_article/comparaison_amplitude_baseline_referee1_2013_ves.png}
    \begin{minipage} [c]  {5in} \scriptsize%
    	    Note: Ratio of the confidence intervals = $ _{}ln(CI_{is}/CI^{ref}_{is})$
    \end{minipage}

    \end{center}
    \end{figure}

   \textbf{XXXX AJouter le complement sur Air et stop XXX} In most cases, the log of the ratio is negative, implying a smaller interval confidence of the $\beta$ estimate with our methodology. Our method thus yields more accurate estimations of the share of additive components, whatever the transport mode considered. We have checked that a similar conclusion applies on other years (they are not reported here for sake of brevity but they are available upon request).
    \end{itemize}

One explanation of the limited accuracy of the alternative method might be the following. Given that the estimation method is run at the country-sector level (exploiting heterogeneity \textit{within} a given country-sector pair), it implicitly assumes that transport costs are independent \textit{across} sectors and \textit{across} origin countries. Put it in plain words, it means that transport costs of say, cars, have nothing in common whether those goods comes from France or from Germany; or that transport costs that apply to imported goods from France have no common component across sectors. This is a disputable assumption. From a statistical point of view, it implies leaving aside information contained in the fact that transport costs have a both a country-specific component and a sector-specific component. We believe that explains the better accuracy of our baseline estimation.

@@

\end{itemize}

All these elements, in particular Concern 2 regarding the lower accuracy of the estimates, drive us to maintain our original estimation as baseline method in the revised version. However, we also want to keep track of this alternative method as further robustness check. For this purpose, we have amended the online Appendix with a section devoted to the referee's method (Section D.3 \textbf{XXX Check XXX}).

@@

\subsubsection{Concerns about endogeneity}

\textit{\textbf{The endogeneity problem}: quoting Footnote 14 of the paper, the authors
are estimating $t_i$ and $t_{s(k)}$ as coefficients on the industry or country
dummies times $1/\widetilde{p}_{ik}$. [...] Based on the productivity-sorting model in Melitz (2003) or the quality-sorting
model in Baldwin and Harrigan (2010),  $1/\widetilde{p}_{ik}$ is either positively
or negatively correlated with $\epsilon_{ik}$. So, the NNLS estimates are biased; and
the bias has nothing to with the casual versus accounting interpretation of
the estimates. Accordingly, the one-line justification the authors provide
to not address the endogeneity problem is far from convincing.}

Indeed, this is a very important point. The referee states that, based on theoretical insights by \citet{melitz} or \citet{baldwin_harrigan}, $1/\widetilde{p}_{ik}$ is correlated in one direction on another with residuals $\epsilon_{ik}$. In other words, more productive firms and/or firms selling high-quality products will charge systematically different prices, all other things equal – in our case, for a given country-product pair.

We obviously do not question this conceptual issue. However, it is worth noting that a good deal of the bias (such as the part relating to the quality effect) is going to appear identically in the CIF (p) and the FAS ($\widetilde{p}_{ik}$) prices. Consequently, since our dependent variable is based on a ratio between the former and the latter, the (reverse causality) bias cancels out. That said, the possibility remains that bigger firms may impact transport costs, due to their ability of bargaining discounts for larger shipped volumes.

Following the referee's advice, we therefore decided to provide a full set of IV estimates to provide a clean assessment of the size of the potential bias. Section 4.3 in the revised version of the paper provides an overview of the results, while section B.4 in Appendix B provides a full presentation of the theoretical basis for the first-stage equation, as well as first-stage estimates. We follow earlier literature (see e.g. Caliendo and Parro, 2015, or Lashkaripour, 2017) by implementing a first-stage equation regressing $\widetilde{p}$ on custom duties coming based on tariffs at the product line, together with one-year lagged fas prices. First-stage estimates reported in section B.4 show that our main instrumental variable displays the right statistical properties, and that we can confidently re-inject the predictions arising from the first-stage equation for $\widetilde{p}_{ik}$ on the right-hand side of Equation 10 to produce a 2SLS-type of estimation. Figure 9 in the revised version of the paper reports our benchmark estimates by transport mode, together with their instrumented counterpart. In all cases, these estimates are very similar. This suggests that our baseline estimates do not suffer any substantial biases arising from endogeneity concerns.

It should be noted that we performed this check on our main dataset (SITC 5 digit), and also at the HS 10 level, to handle simultaneously the referee's concern about aggregation issues. In the latter case, second-stage estimates are not reported for the sake of space, but do not change anything to previous conclusion - they are very similar to their non-IV, least squares counterparts. Needless to say that these results are available upon request.

@@

\subsubsection{The aggregation problem}

\textit{\textbf{The aggregation problem}: The original annual Census data reports
trade at the origin country-HS10 product-district level of aggregation,
whereas the authors are aggregating up the data even further to the origin
country-HS5 industry-year level. Such an aggregation comes with strong implicit assumptions and sacrifices a lot of useful variation in the data.
The authors are motivating the aggregation by stating that the problem
would become computationally expensive without it. But this reasoning
brings us back to my original point that the authors can use the Hummels'
Methodology to circumvent the computational burden.}

It is true that the original annual Census data reports trade at the origin country-HS 10 product-district level of aggregation. Our initial choice of retaining $s=3$ at the sectoral level, $k=5$ at the product level was driven by the use of Hummels' dataset available over 1974-2004 with $k=5$ the finest degree of aggregation. We agree with the referee that jumping from $k=10$ to $k=5$ digits at the product level is detrimental to our ability to exploit useful variations in the data. After checking with the US Bureau of Census, HS-10 data is only available since 1989, now available to 2019. As previously mentioned, due to the Covid situation, it was further only possible to receive the data over the years 1997-1999 and from 2001 onwards.We decided to maintain the case $s=3, k=5$ as baseline, and to run the estimation using 10-digit products in the new Sub-Section 3.3.3 \textbf{XXX CHECK XXX }devoted to robustness analysis.

@@

\subsection{Critique 2: Calculation of Unit Prices}

\textit{My second critique concerns the way the authors are calculating the unit prices.
The Census data reports the quantity of goods per observation. So, the authors
can calculate the unit price as Value/Quantity, which is consistent with how
price is modeled in standard trade models. Instead, the authors calculate unit
price as Value/Weight. This used to be a common exercise in the past where
many data-sets did not report Quantity. But, given their data, there is no
justification for the authors to calculate the prices this way.}

\textit{Calculating the unit price as Value/Weight presents the authors
with an additional endogeneity problem. To elaborate, let $\omega_{ik} = Weight/Quantity$
denote the unit weight of the goods in observation $ik$. [...] There is evidence that (i) $\omega_{ik}$ varies significantly within narrowly-defined product
categories, and (ii) $\omega_{ik}$ is negatively correlated with transport costs. So the
way the authors are calculating unit prices and estimating the model creates a
new (but avoidable) source of endogeneity.}

% MEMO: DO NOT FORGET TO REPORT THE ARGUMENTATION BELOW IN THE MAIN TEXT XXX
\paragraph{Our answer:}
\noindent %This is a very important point, and we thank the referee for raising it.
The referee definitely raised a very important point here, and indeed, Census data do report the quantity of goods (and sometimes even two quantities).
%At a more fundamental level, this raises the following question: Do we have reason to believe our measure of unit prices generate significant deviations from the one relying on quantities?
In this context, the findings in \cite{Lashkaripour_JIE2020} are specifically enlightening.
Based on US data very similar to ours over the period 1995-2015, the paper highlights, among other results, that the unit weight of imported goods is indeed substantially heterogeneous even within narrowly-defined product categories and that the cost of transportation increases more rapidly with unit weight than the cost of production. \cite{Lashkaripour_JIE2020} finds that accounting for the heterogeneity in export unit weights provides evidence in favor of the ad-valorem cost assumption regarding transport costs.
This result of transport costs close to be totally ad-valorem contrasts from our own findings of additive costs representing 30 to 45\% of total costs. There are explanations for this difference. Beyond a longer time span, our database is exhaustive, and encompasses all goods and industries, while \citet{Lashkaripour_JIE2020}) restricts to indivisible/discrete goods that represent a bit more 56\% of US total imports of goods in his dataset. In this regard, when comparing Tables 1 and 10 in \citet{Lashkaripour_JIE2020}, one can see that the share of multiplicative costs tends to decrease with the share of discrete goods. It is therefore reasonable to think that the inclusion of all goods, like in our setting, would move the average share of multiplicative costs away from 100\%.

Nevertheless, considering the importance of the referee's remark, we went beyond this very first argument to investigate this question in depth. We first discuss data and estimation difficulties before giving the results. At a more fundamental level, we argue that looking at transport costs on a per-weight basis does add relevant information.

@@

%The two stories are not necessarily incompatible, however.

%Nevertheless, the point made by the referee is an important one and deserves careful investigation. We devoted a lot of thought to a potential switch from weight to quantity.
%Running the estimation considering quantities (i.e., units) rather than weight, still on the transport mode-yearly basis yet appears really uneasy in our context for several, non-trivial reasons, that we develop below.

\subsubsection{Data availability issue}

The first difficulty is availability of information on quantities. Neither the US Bureau of Census data nor the 1974-2004 Hummels's data (based on the Census Bureau data) report the quantity by transport mode. This is incompatible with our empirical strategy of estimation which is conditional on the transport mode, similarly as in \cite{hummels2007}. As a result, computing the unit price of all trade flows would require the assumption that the weight per unit is the same for vessel shipments and air shipments at the level of the observation. This is unlikely, as one would expect the higher-to-weight value to be transported by air rather than by vessel. The alternative is only to consider single-mode flows. In Hummels's data (1974-2014), on average 41.1 \% of trade flows and 79\% of trade value are multi-mode. This would reduce the total value of the sample from 12,500 billion dollars to 2,650 billion dollars, entailing a large loss of useful information. Original census data, when accessible, are more promising.\footnote{Original Census data are  reported at the HS-10 digit $\times$ district of entry $\times$ district of unleading $\times$ rate provision code.} In 2019, multi-modal flows are 570 billion dollars out of 1,790 billion dollars, or 31\% of the data. This is still a large share, but not too large to preclude any work. Accordingly, we dig deeper into this issue with the US Census dataset, restricted to single transport mode flows. \smallskip

Quantity units are a second difficult. The Census data remain silent on that matter. To the best of our knowledge, these can only be found in the ``Harmonized Tariff Schedule of the United State''. Unfortunately, these schedules change many time per year and only the schedules from 2009 onwards are available in a .csv format on the Census website. On the years for which the match could be done (from 2009), it turns out that at our sector level (3-digit), goods (either at the 5-digit or the 10-digit level) are measured in different units. In 2019, only 125 3-digit sectors out of 230 are measured in a single unit (after cleaning up the unit names\footnote{As units are not always coherent (eg weight can be given in ``kg’’, ``kg.'' ``Kg'' and, also, ``g'' and ``t'').}).\footnote{For instance, 3-digit SITC sector ``061 Sugar, molasses and honey'' includes among other products, 5-digit SITC product ``6150 Molasses, whether or not decolourized'', measured in liters and 5-digit SITC product ``06160 Natural Honey'' measured in kg. Actually worse than this, the 5-digit SITC product ``06190 Other sugars; sugar syrups; artificial honey (whether or not mixed with natural honey); caramel'' includes both 10-digit HTS product ``1702903500 Other: invert molasses'', measured in liters and 10-digit HTS product ``1702602200 Blended syrups described in additional u.s. note 4 to chapter 17: described in general note 15 of the tariff schedule and entered pursuant to its provisions''  measured in kg.} Neglecting these differences would invalidate our functional forms, as no one expects the transport cost of a ``piece'' to be the same as the transport cost of a ``kg'', even in the same sector.
So we are limited to using quantity units from 2009 to 2019, amending our structure of fixed effects to consider the triplet (origin country, sector, quantity unit).

@@

\subsubsection{Estimation issue}

Getting deeper on the estimated functional form raised another difficulty in adapting our equation to per-unit rather than per-weight prices. As discussed above, in our baseline regression we separate each transport cost component in two distinct sector-origin country dimensions. As in \cite{Irrazabal_2015}, we assume an additive form for the additive cost, i.e. $t_{is(k)} = t_i+t_{s(k)}$ with $i$ the origin country and $s$ the sector. In the specific case of quantities, this raises a non-trivial issue for country-level fixed effects. Sector-level fixed effects could be easily replaced by (sector, quantity unit) fixed effects; but the same does not appear relevant for country fixed effects. Let us elaborate on this issue.

In the per-weight price, the existence of a single country fixed effect applicable to all sectors is justified, as a kilogram is always a kilogram and one can assume they both add the same to transport costs from, say, Germany. In contrast, an unit of tee-shirt is quite different from an unit of car. To clarify this point, consider imports of tee-shirts and cars from Germany and China. Under the separability assumption, importing a tee-shirt from either country implies paying the cost given by both countries fixed effect (the same for all sectors) and the cost given by the sector fixed effect ; and similarly for importing a car. Hence, the difference in the cost of importing a car from Germany versus China would be the same, in dollars, as the difference between the cost of importing a tee-shirt from Germany relative to China. This does not seem a sensible assumption. In this setting, we cannot keep the separability assumption.
As discussed before, this dramatically increases the computational difficulty of our method (with no substantial different results, see Subsection 3.3.1. in the main paper).\smallskip

Integrating these various constraints, we run the robustness check (weight versus quantity) \textit{i)} on a sample reduced over 2009-2019, considering single transport mode flows - amounting to 66\% of the value of the baseline sample; \textit{ii)} retaining a non-separable structure of three-dimensional fixed effects $t_{is(k)u}$, $\tau_{is(k)u}$ according to the following equation:
\begin{equation*}
\ln\left(\frac{p_{iku}}{\widetilde{p}_{iku}}-1 \right)= \ln \left(\tau_{is(k)u} -1+\frac{t_{is(k)u} }{\widetilde{p}_{iku}} \right) + \epsilon_{iku}
\end{equation*}
\noindent where $p_{iku}$ refers to the cif price associated with quantity of goof $k$ imported from country $i$, measured in unit $u$, $\widetilde{p}_{iku}$ the corresponding unit value (fas price).

### 2021-11-22 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

The results are reported in Table \ref{tab_comp_wgt_qty} and in Figure \ref{graph_comp_wgt_qty} (as well as in the online appendix D.4). In Table \ref{tab_comp_wgt_qty}, for each transport mode, the first column reports the estimation based on the price per quantity, the second column reports the results obtained considering the price per kg on the same sample and the last column reported our baseline results on the large sample (considering the average value over 2005-2019, under the separability assumption).

@@

\begin{table}[htbp]
	\caption{Comparison: Price per quantity versus per kg, 2009-2019}
	\begin{center}		
		\input{../../revised_article/Online_Appendix/Comp_baseline_wgt_qy_reshaped.tex}
%		\input{../../revised_article/Online_Appendix/Comp_baseline_wgt_qy.tex}
{\parbox[l]{12cm}{ \vspace{4pt}\footnotesize{Notes: Time trend coefficient is the annual growth rate.}}}
\end{center}
	\label{tab_comp_wgt_qty}%
\end{table}%

\begin{figure}[htbp]
	\caption{$\beta$ Estimate: Price per quantity or price per kg, 2009-2019}
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[height=8cm]{../../revised_article/scatter_chronology_non_separe_wgt_non_separe_qy.png}\\
			\multicolumn{2}{l}{{\footnotesize Notes: In both cases, estimation is run without imposing the separability assumption.}}
		\end{tabular}
	\end{center}
		\label{graph_comp_wgt_qty}%
\end{figure}

Two main results emerge. First, given the constraints on the sample selection for quantities, the estimation based on quantity can only be run on a reduced sample. In contrast to the aggregation and the separability issues, these restrictions that strongly limit both the number of sectors and of countries covered, do also impact the value of trade flows covered. In our view, this raises a non-trivial sample selection bias that reduces the general scope of the transport cost estimates. Second, in terms of $\beta$ estimates, the results show clearly that using price per unit (whatever that unit is) instead of price per weight decreases the share of additive costs (except if one look at the median for air). In this regard, they stand in line with the results of \cite{Lashkaripour_JIE2020}, and confirm the correlation between weight per unit and unit price. Still, the share of additive cost is not reduced to zero (except if one looks at the median for vessel). Thus these results do not disqualify our approach, especially as we cover a much larger period and sample with our baseline estimate.

\subsubsection{On the relevance of the price per-weight approach}
At a more fundamental level, we do believe that the study of transport costs measured on a per-weight price add some relevant information on the international transport cost burden faced by exporters. Let us explain why.

Our main objective is to provide a quantitative assessment of the international transport costs burden over time; on that matter, one may start with the observation that transport cost schedules are expressed through a mixed, per-weight and per-volume basis, both historically and nowadays. For example, in 2021, air freight trade costs are expressed in weights, with a minimal weight per volume (``volumetric weight'' or ``dimensional weight'')\footnote{See for example \href{https://transporteca.co.uk/shipping-costs}{https://transporteca.co.uk/shipping-costs}, \href{http://wap.dhl.com/serv/volweight.html}{http://wap.dhl.com/serv/volweight.html} and \href{https://en.wikipedia.org/wiki/Dimensional_weight}{ https://en.wikipedia.org/wiki/Dimensional\_weight}).} while maritime freight costs are expressed in volume.
Hence, looking at per-kg transport cost can be interpreted straightforwardly as trying to estimate the actual existing shipping costs, with sector fixed effects interpretable as measure of mean density for different sectors. The existence of per-volume or per-weight shipping cost is directly linked to the technical constraints of the transportation sector, hence exogenous to exporting firms' decisions - in contrast, per-unit shipping cost depends on the behavior of exporting firms. Put differently, the shipping cost per weight is one of the exogenous parameters firms take into account in their production choices, including weight per unit. Accordingly, studying the technical per-volume or per-weight shipping cost is interesting to understand the context in which firms operate.

Another argument is illustrated by Figure \ref{graph_Share_of_discrete_goods.png}. After computing the share of discrete goods per 5-digit SITC import in 2009, we have used the changing composition of US imports to approximate the share of discrete goods in the total value of US imports on a yearly basis. According to this rough approximation, discrete goods are between 23\% and 52\% of US imports, reaching a value above 50\% for only two years. Switching to a per-unit approach would hence mean a marked reduction in the trade flows coverage, thereby limiting the general scope of our estimates.

@@

After considering all the above arguments in depth, we decided not to switch the paper from the study of price per weight to the study of price per quantity. We thus maintained our original empirical strategy covering the whole period 1974-2019 in the revised version, while we extended the online Appendix with this supplementary robustness check. We hope to have convinced you that this is a relevant choice.

\subsection{Critique 3: Big Picture Implications}

\textit{My third critique concerns the lack of an exciting punchline. The fact that
composition effects have not countervailed the reduction in pure transport costs
(at least not as much as previously believed) is an interesting but minor observation.
Does this observation revise our understanding of say the gains from
trade? Does it shed new light on a puzzle many people are thinking about?
One crude suggestion is to see how the reduction in the industry-specific cost
terms is related to the industry-level trade elasticities. If the composition effects
favor low-elasticity industries, the findings in the paper may have first-order
implications for the gains from trade.
Another suggestion is to dig deeper into the relative rate at which additive
and multiplicative transport costs have declined over time. Since additive transport
costs favor rich (high-quality exporting) countries, the disproportionally
greater reduction in additive costs can perhaps explain the rise of low-income
exporter as documented by Hanson (2012, JEP).}

\paragraph{Our answer:}
\noindent We devoted a lot of thought to this point, which directly echoed a similar concern by the other referee. Taking stock of your suggestion, we decided to offer insights on the welfare implications of our results. The new section 5 ``The role of additive cost: Theoretical insights'' is devoted to a theory-based analysis of the alterations to welfare gains involved by the relative variations of additive and multiplicative transport costs over our period of analysis. To do so, we start from the canonical \cites{melitz} model where we add additive trade costs. The inclusion of additive costs in a \citet{melitz} setting has already been performed in \citet{sorensen2014} and \citet{Irrazabal_2015}. However, \citet{sorensen2014} exclusively performs a theoretical analysis, without any quantitative exercise. In addition to a partial equilibrium extension of \citet{melitz}, \citet{Irrazabal_2015} do perform a quantitative simulation to assess the welfare variations induced by the presence of additive costs, but the latter is based on a calibration for transport costs restricted to 2004, based on the case of Nowrway. In contrast, our own exercise relies on a several decades time span for the US, allowing us to highlight the welfare alterations induced over time by the relative dynamics of additive and multiplicative costs, based on ``true'' values for the latter - remember that our methodology allows for the identification of both multiplicative and additive costs as a share of total costs, whereas additive costs in \citet{Irrazabal_2015} are expressed relatively to the (median) export price.

More precisely, we use some of the estimates underlying results reported in Section 3 concerning multiplicative and additive costs, more precisely those for the years 1974 and 2019. Based on the latter, we implement several comparative statics exercises to investigate the different welfare consequences of alterations to multiplicative and additive costs. In addition, we also assess how the latter results are distorted by changes in sunk costs of exports, $f_{x}$. To that end, we adjust the share of exporting firms in the US: Based on \citet{Lincoln_McCallum2018}, we set the latter to 35\% in 2019, versus 21\% in 1974. In our preferred exercise, we quantify the welfare gains that derive from the reduction in transport costs as documented in Section 3, relying on a combined reduction in each additive/ad-valorem component, with the reduction in the fixed export cost. We compare this with the case where the total transport costs reduction is solely attributed to a decrease in ad-valorem costs.

### 2021-11-22 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

After considering all the above arguments in depth, we decided not to switch the paper from the study of price per weight to the study of price per quantity. We thus maintained our original empirical strategy covering the whole period 1974-2019 in the revised version, while we extended the online Appendix with this supplementary robustness check. We hope to have convinced you that this is a relevant choice.

\subsection{Critique 3: Big Picture Implications}

\textit{My third critique concerns the lack of an exciting punchline. The fact that
composition effects have not countervailed the reduction in pure transport costs
(at least not as much as previously believed) is an interesting but minor observation.
Does this observation revise our understanding of say the gains from
trade? Does it shed new light on a puzzle many people are thinking about?
One crude suggestion is to see how the reduction in the industry-specific cost
terms is related to the industry-level trade elasticities. If the composition effects
favor low-elasticity industries, the findings in the paper may have first-order
implications for the gains from trade.
Another suggestion is to dig deeper into the relative rate at which additive
and multiplicative transport costs have declined over time. Since additive transport
costs favor rich (high-quality exporting) countries, the disproportionally
greater reduction in additive costs can perhaps explain the rise of low-income
exporter as documented by Hanson (2012, JEP).}

\paragraph{Our answer:}
\noindent We devoted a lot of thought to this point, which directly echoed a similar concern by the other referee. Taking stock of your suggestion, we decided to offer insights on the welfare implications of our results. The new section 5 ``The role of additive cost: Theoretical insights'' is devoted to a theory-based analysis of the alterations to welfare gains involved by the relative variations of additive and multiplicative transport costs over our period of analysis. To do so, we start from the canonical \cites{melitz} model where we add additive trade costs. The inclusion of additive costs in a \citet{melitz} setting has already been performed in \citet{sorensen2014} and \citet{Irrazabal_2015}. However, \citet{sorensen2014} dose not perform an empirically based quantitative exercise. In addition to a partial equilibrium extension of \citet{melitz}, \citet{Irrazabal_2015} do perform a quantitative simulation to assess the welfare variations induced by the presence of additive costs, but the latter is based on a calibration for transport costs restricted to 2004, based on the case of Norway. In contrast, our own exercise relies on a several decades of US data. It allows us to compute the welfare effect of  taking intor account the relative dynamics of additive and multiplicative costs. Furthermore, our methodology allows for the identification of both multiplicative and additive costs as a share of total costs, whereas additive costs in \citet{Irrazabal_2015} are expressed relatively to the sum of prices and multiplicative costs.

More precisely, we use the estimates underlying results reported in Section 3 concerning multiplicative and additive costs, to implement several comparative statics exercises to investigate the different welfare consequences of alterations to multiplicative and additive costs. In addition, we also assess how the latter results are distorted by changes in sunk costs of exports, $f_{x}$. To that end, we adjust the share of exporting firms in the US. Based on \citet{BEJK-AER-03, Lincoln_McCallum2018}. In our preferred exercise, we quantify the welfare gains that derive from the reduction in variable transport costs as documented in Section 3, relying on a combined reduction in each additive/ad-valorem component in a context of fixed export cost reduction. We compare this with the case where the reduction of total transport costs  is solely attributed to a decrease in ad-valorem costs.

Table 5 in Section 5 of the paper reports the results of these various comparative statics exercises for Air and Vessel transport modes. Specifically, we report the welfare effect of change in total transport costs decomposed in its two dimensions (additive and ad-valorem),both in absolute and in relative terms. We have two major insights. First, using the reduction of transport costs in vessel (air),  welfare gains are around 50\% (14\%) higher when this reduction is achieved through the estimated reduction in additive and ad-valorem costs. Second, the decrease in export sunk costs (i.e., increase in the share of exporting firms) proportionally amplifies the gains from decreasing variable costs, with again an additional premium coming from the decrease of additive costs.

Overall, these results add a substantial contribution to the paper : We are able to provide a quantitative assessment of the welfare gains induced by the decrease in both types (additive and multiplicative) of costs over a 45-year period, and to highlight the respective part of each component in the determination of these gains.
%Note also that not only the inclusion of additive costs in the underlying framework generates large welfare differences, but also that the latter are probably a lower bound of the welfare variations induced by changes in additive \emph{trade} costs, larger than the sole transport costs.

### 2021-11-23 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee1.tex

\subsubsection{Estimation issue}

Getting deeper on the estimated functional form raised another difficulty in adapting our equation to per-unit rather than per-weight prices. As discussed above, in our baseline regression we separate each transport cost component in two distinct sector-origin country dimensions. As in \cite{Irrazabal_2015}, we assume an additive form for the additive cost, i.e. $t_{is(k)} = t_i+t_{s(k)}$ with $i$ the origin country and $s$ the sector. In the specific case of quantities, this raises a non-trivial issue for country-level fixed effects. Sector-level fixed effects could be easily replaced by (sector, quantity unit) fixed effects; but the same does not appear relevant for country fixed effects. Let us elaborate on this issue.

In the per-weight price, the existence of a single country fixed effect applicable to all sectors is justified, as a kilogram is always a kilogram and one can assume they both add the same to transport costs from, say, Germany. In contrast, an unit of tee-shirt is quite different from an unit of car. To clarify this point, consider imports of tee-shirts and cars from
Germany and China. Under the separability assumption, importing a tee-shirt from either country implies paying the cost given by the  country fixed effect (the same for all sectors) plus the cost given by
the sector fixed effect ; and similarly for importing a car.
Hence, the difference in the cost of importing a car from Germany versus China would be the same, in dollars, as the difference between the cost of importing a tee- shirt from Germany relative to China. This does not seem a sensible assumption.
In this setting, we cannot keep the separability assumption.
As discussed before, this dramatically increases the computational difficulty of our method (with no substantial different results, see Subsection 3.3.1. in the main paper).\smallskip
